---
title: "Hiawatha National Forest Ecological Assessment, 2023 "
---

## Goals of this assessment

In general we will use [LANDFIRE](https://landfire.gov/) and [Center for Resilient Conservation Science](https://crcs.tnc.org/) products to:

1. Map and summarize past and present ecosystems and ecosystem conditions
2. Explore historical disturbance regimes
3. Summarize patterns of change and management opportunities
4. Present maps of landscape-scale connectivity and resilient sites

## Location of this assessment

The assessment area is essentially the Hiawatha National Forest Proclamation Boundary plus a 1 mile buffer (supplied by Sam Adams, GIS coordinator).  

<br>

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}

library(foreign)
library(sf)
library(terra)
library(tidyverse)
library(raster)


```


```{r read shapefile, message=FALSE, warning=FALSE, include=FALSE}
#  read shape
shp <- st_read("data/hiawathaFuels.shp") %>% 
  st_transform(crs = 5070) %>%
  st_union() %>%
  st_sf()
```

```{r locator map, message=FALSE, warning=FALSE, echo=FALSE}
library(tmap)

# toggle tmap mode to interactive viewing
tmap_mode("view")

# read area of interest shapefile
# shp <- st_read("./DATA/gmnf_ownership.shp") %>%
#   st_transform(5072) %>%
#   st_union() %>%
#   st_sf()

# create a quick interactive map
quickmap <- qtm(shp, borders = "darkgreen",  check.and.fix = TRUE)

quickmap



```


