---
title: "Hiawatha National Forest Ecological Assessment, 2023"
author: "Randy Swaty with substantial code contributions from Myles Walimaa"
---

## Goals of this assessment

In general we will use [LANDFIRE](https://landfire.gov/) and [Center for Resilient Conservation Science](https://crcs.tnc.org/) products to:

1. Map and summarize past and present ecosystems and ecosystem conditions
2. Explore historical disturbance regimes
3. Summarize patterns of change and management opportunities
4. Present maps of landscape-scale connectivity and resilient sites

Outputs presented here are the tip of the iceberg of what can be done with these datasets and are intended to help begin brainstorming about appropriate questions that could be explored collaboratively.


## Interacting with this Web-Hosted Information Tool (WHIT)
A few notes about using this site:
* This platform is web-hosted so you can simply share a link with collaborators for their review.  https://rswaty.github.io/hiawatha2023/
* Maps and charts are intended to represent general patterns, and are almost always limited to most common types (e.g., ecosystems).  You can use the "zoom" tool to take a closer look.
* All maps, input datasets and further assistance can be obtained by contacting the author, [Randy Swaty](mailto:rswaty@tnc.org).


## Location of this assessment

The assessment area is essentially the Hiawatha National Forest Proclamation Boundary plus a 1 mile buffer (supplied by Sam Adams, GIS coordinator).  

<br>

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}

library(foreign)
library(sf)
library(terra)
library(tidyverse)
library(raster)


```


```{r read shapefile, message=FALSE, warning=FALSE, include=FALSE}
#  read shape
shp <- st_read("data/hiawathaFuels.shp") %>% 
  st_transform(crs = 5070) %>%
  st_union() %>%
  st_sf()
```

```{r locator map, message=FALSE, warning=FALSE, echo=FALSE}
library(tmap)

# toggle tmap mode to interactive viewing
tmap_mode("view")

# read area of interest shapefile
# shp <- st_read("./DATA/gmnf_ownership.shp") %>%
#   st_transform(5072) %>%
#   st_union() %>%
#   st_sf()

# create a quick interactive map
quickmap <- qtm(shp, borders = "darkgreen",  check.and.fix = TRUE)

quickmap



```


