---
title: "Hiawatha National Forest Ecological Assessment, 2023"
author: "Randy Swaty with substantial code contributions from Myles Walimaa"
---

## Goals of this demonstration

We will use [LANDFIRE](https://landfire.gov/){target="blank"} products to:

1. Characterize and map past and present ecosystem conditions
2. Explore historical disturbance patterns
3. Summarize patterns of change and management opportunities


The following charts, maps, and graphs are based on current LANDFIRE products, and provide a starting point for further analysis.

This demonstration will:

* Provide context for the past and present ecosystem conditions the Hiawatha National Forest
* Demonstrate the power of data visualization to explore ecological patterns and functions using LANDFIRE products
* Facilitate an understanding of historical and current conditions on a regional scale

## Location

The assessment area is essentially the Hiawatha National Forest Proclamation Boundary plus a 1 mile buffer (supplied by Sam Adams, GIS coordinator).  

<br>

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}

library(foreign)
library(sf)
library(terra)
library(tidyverse)
library(raster)


```


```{r read shapefile, message=FALSE, warning=FALSE, include=FALSE}
#  read shape
shp <- st_read("data/hiawathaFuels.shp") %>% 
  st_transform(crs = 5070) %>%
  st_union() %>%
  st_sf()
```

```{r locator map, message=FALSE, warning=FALSE, echo=FALSE}
library(tmap)

# toggle tmap mode to interactive viewing
tmap_mode("view")

# read area of interest shapefile
# shp <- st_read("./DATA/gmnf_ownership.shp") %>%
#   st_transform(5072) %>%
#   st_union() %>%
#   st_sf()

# create a quick interactive map
quickmap <- qtm(shp, 
                borders = "darkgreen", 
                fill = NULL, 
                check.and.fix = TRUE, 
                basemaps = 'https://server.arcgisonline.com/ArcGIS/rest/services/World_Topo_Map/MapServer/tile/{z}/{y}/{x}',
                title = 'Wyoming Sagebrush Subregion',)

quickmap



```


